Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-05-24 source/main.tex
partial cvx smth nasgd
reorg
Update main.tex
refine proof v1.
overview re arrange.
add experiments section
add strongly convex results
first draft
add abstract v1

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsthm}     % for theorems
\usepackage{algorithm,algorithmic}
\usepackage{mathtools}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{amssymb}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\usepackage{balance}

\newcommand{\eq}[1]{{Eq~(#1)}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}
\newcommand{\lkxcom}[1]{{\color{red}{#1}}}
\input{bmacros}
\newtheorem*{assumption*}{Assumption}

@@

% \tableofcontents
% \begin{abstract}
% \end{abstract}

%% Note for ICLR'20 paper
% \input{note_sec_problem}
% \input{note_sec_algorithm}
% \input{note_sec_part}
% \input{note_sec_q}

% converge proof
\input{sec_problem}
\input{sec_overview}
\newpage
% \input{sec_acceleratedFL}
% \input{sec_cvxnonsm}

@@

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsthm}     % for theorems
\usepackage{algorithm,algorithmic}
\usepackage{mathtools}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{amssymb}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\usepackage{balance}
\usepackage{comment}
\newcommand{\eq}[1]{{Eq~(#1)}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newtheorem{theorem}{Theorem}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}
\newcommand{\lkxcom}[1]{{\color{red}{#1}}}

\newcommand{\ov}[1]{{\overline{\mathbf{#1}}}}
\input{bmacros}
\newtheorem*{assumption*}{Assumption}

@@

% \tableofcontents
\begin{abstract}
Federated learning is a distributed learning paradigm that enables learning a
model jointly over a large number of workers without sharing the private data
on local workers. The characteristics of non-identically distributed data
across the network and low device participation bring significant challenges
in analyzing the convergence of federated learning algorithms. Prior works
mainly analyze its convergence rate in limited scenarios.
In this work, we provide a comprehensive analysis of the convergence rate of SGD and Nesterov SGD for general convex problems.
Theoretically, we firstly show 
that the convergence rates enjoy a linear speedup for
all convex smooth problems for both algorithms.
Furthermore, we propose a new accelerated SGD algorithm improving the convergence rate over SGD in the overparameterized setting. 
Empirical evaluation of the algorithms in various settings match our theoretical
results.
\end{abstract}

% converge proof
% Introduction.

% accelerated 
% convex strongly 
% smooth non-smooth. 
\input{sec_problem}
\input{sec_theorems}
\newpage
\input{sec_exp}
\input{sec_exp_note}

\newpage
\appendix
\input{sec_overview}
% \input{sec_acceleratedFL}

@@

% paper

% \begin{itemize}
% 	\item On Federated Learning of Deep Networks from Non-IID Data: Parameter Divergence and the Effects of Hyperparametric Methods: empirical evaluation 
% 	paper, the loss surface could be helpful.
% 	\item On the Linear Speedup Analysis of Communication Efficient Momentum SGD for Distributed Non-Convex Optimization: Non-convex, smooth, accelerated SGD, Full device particaption.
% \end{itemize}
